All the concepts behind TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages (Draft)

### 2020-12-14 article.tex
TTT: una palabra importante

      }  
  }
  \caption{
  \en{Schematic representation of a single causal model for the entire history of events.}
  \es{Representaci\'on esquemática de un único modelo causal para toda la historia de eventos.}
  %
  \en{Only the neighbors of a sequence of estimates are displayed.}
  \es{S\'olo se muestra los vecinos de una secuencia de estimaciones.}
  %
%   \en{Its probabilistic solution generates the approach known as \emph{smoothing}, in which historical information flows through the whole system.}
%   \es{La soluci\'on probabil\'istica da como resultado el abordaje conocido como \emph{smoothing}, en el que la informaci\'on hist\'orica fluye por todo el sistema.}
%   %
%   %\en{These types of models are known as \emph{state-space models}.}
%   %\es{Este tipo de modelos se conocen como \emph{state space models}.}
  }
  \label{fig:smoothing}
\end{figure}
%
\en{By applying the rules of probability to this temporal model, historical information naturally propagate throughout the system, solving the problems of the filtering approach.}
\es{Al aplicar las reglas de la probabilidad sobre este modelo temporal, la informaci\'on hist\'orica propaga naturalmente hacia todo el sistema, resolviendo los problemas del enfoque de filtro.}
%
\en{A prior distribution at an event $t$, with $\gamma = 0$, is now the product of all past and future information.}
\es{La distribuci\'on a prior en un evento $t$, con $\gamma = 0$, es ahora la multiplicaci\'on de toda la informaci\'on pasada y futura.}
%
\begin{equation}\label{eq:smooth_prior}
 \text{Prior}_{i_t} = \text{Prior}_{i_0} \underbrace{\prod_{k = 1}^{t-1} \text{\en{Likelihood}\es{Verosimilitud}}_{i_k}}_{\text{\en{Past information}\es{Informaci\'on pasada}}} \underbrace{\prod_{k = t + 1}^{T} \text{\en{Likelihood}\es{Verosimilitud}}_{i_k}}_{\text{\en{Future information}\es{Informaci\'on futura}}}
\end{equation}
%
\en{This generates a mutual dependency between likelihoods, forcing us to implement an eficiente iterative algorithm to solve inference (details at secci\'on~\ref{sec:throguthTime})}
%
\es{Esto genera una mutua dependencia entre verosimilitudes, obligándonos a implementar un algoritmo para resolver la inferencia (detalles en la secci\'on~\ref{sec:throguthTime}).}
%
\en{The loopy belief propagation is procedure that converge with a few linear iterations over the data, scaling to millions of observations in a few minutes.}
\es{Este procedimiento converge con unas pocas iteraciones lineales sobre los datos, escalando a millones de observaciones en pocos minutos.}
%
\en{At the beginning, the likelihoods that are not yet defined are initialized with a neutral value or simply excluded.}
\es{Al empezar, las verosimilitudes que aun no están definidas se inicializan con un valor neutro o simplemente se las excluy\'e.}
%
\en{In Figure~\ref{fig:smooth_example} we show the behavior of the estimates in a data set with two agents and two events.}
\es{En la figura~\ref{fig:smooth_example} se muestra el comportamiento de las estimaciones en conjunto de datos de dos agentes y dos eventos.}
%
\begin{figure}[h!]
  \centering
  \scalebox{.9}{
    \tikz{ %
      \node[latent] (s10) {$s_{a_0}$} ;
      %
      \node[latent,  below=of s10,yshift=-1cm] (s11) {$s_{a_1}$} ;

>>>>

      }  
  }
  \caption{
  \en{Schematic representation of a single causal model for the entire history of events.}
  \es{Representaci\'on esquemática de un único modelo causal para toda la historia de eventos.}
  %
  \en{Only the neighbors of a sequence of estimates are displayed.}
  \es{S\'olo se muestra los vecinos de una secuencia de estimaciones.}
  %
%   \en{Its probabilistic solution generates the approach known as \emph{smoothing}, in which historical information flows through the whole system.}
%   \es{La soluci\'on probabil\'istica da como resultado el abordaje conocido como \emph{smoothing}, en el que la informaci\'on hist\'orica fluye por todo el sistema.}
%   %
%   %\en{These types of models are known as \emph{state-space models}.}
%   %\es{Este tipo de modelos se conocen como \emph{state space models}.}
  }
  \label{fig:smoothing}
\end{figure}
%
\en{By applying the rules of probability to this temporal model, historical information naturally propagate throughout the system, solving the problems of the filtering approach.}
\es{Al aplicar las reglas de la probabilidad sobre este modelo temporal, la informaci\'on hist\'orica propaga naturalmente hacia todo el sistema, resolviendo los problemas del enfoque de filtro.}
%
\en{A prior distribution at an event $t$, with $\gamma = 0$, is now the product of all past and future information.}
\es{La distribuci\'on a prior en un evento $t$, con $\gamma = 0$, es ahora la multiplicaci\'on de toda la informaci\'on pasada y futura.}
%
\begin{equation}\label{eq:smooth_prior}
 \text{Prior}_{i_t} = \text{Prior}_{i_0} \underbrace{\prod_{k = 1}^{t-1} \text{\en{Likelihood}\es{Verosimilitud}}_{i_k}}_{\text{\en{Past information}\es{Informaci\'on pasada}}} \underbrace{\prod_{k = t + 1}^{T} \text{\en{Likelihood}\es{Verosimilitud}}_{i_k}}_{\text{\en{Future information}\es{Informaci\'on futura}}}
\end{equation}
%
\en{This generates a mutual dependency between likelihoods, forcing us to implement an eficiente iterative algorithm to solve inference (details at secci\'on~\ref{sec:throguthTime})}
%
\es{Esto genera una mutua dependencia entre verosimilitudes, obligándonos a implementar un algoritmo para resolver la inferencia (detalles en la secci\'on~\ref{sec:throguthTime}).}
%
\en{The expectation propagation defines a procedure that converge with a few linear iterations over the data, scaling to millions of observations in a few minutes.}
\es{Este procedimiento converge con unas pocas iteraciones lineales sobre los datos, escalando a millones de observaciones en pocos minutos.}
%
\en{At the beginning, the likelihoods that are not yet defined are initialized with a neutral value or simply excluded.}
\es{Al empezar, las verosimilitudes que aun no están definidas se inicializan con un valor neutro o simplemente se las excluy\'e.}
%
\en{In Figure~\ref{fig:smooth_example} we show the behavior of the estimates in a data set with two agents and two events.}
\es{En la figura~\ref{fig:smooth_example} se muestra el comportamiento de las estimaciones en conjunto de datos de dos agentes y dos eventos.}
%
\begin{figure}[h!]
  \centering
  \scalebox{.9}{
    \tikz{ %
      \node[latent] (s10) {$s_{a_0}$} ;
      %
      \node[latent,  below=of s10,yshift=-1cm] (s11) {$s_{a_1}$} ;
